### 2019-09-09 reports/thesis/book.tex
Revise

The uncertainty of the projection was modelled using a compound Poisson distribution. This arises from x-ray photon arrivals being a Poisson process and each photon has random energy. This resulted in a linear relationship between the mean and variance of the grey value in the projection. Fitting of the compound Poisson distribution using the expectation-maximisation algorithm was unsuccessful due to identifiability issues with the model. Instead, a gamma distributed generalised linear model was fitted and used for variance prediction to quantify the uncertainty.

Software, called \emph{aRTist}, was used to simulate the projection and compared with the obtained projection in the face of uncertainty by treating each pixel as a hypothesis test. To overcome the imperfections of the simulation, the empirical null filter was used to cater for model misspecification so that sensible inference was achieved. This was done by locally normalising the test statistics using the mode. Voids with diameters in the order of millimetres were detectable.

@@

The main aim of this thesis is to investigate if it is possible to do quality control of additive manufactured products using only a few x-ray projections to speed up the quality control process. By using fewer x-ray projections, uncertainty is introduced. This is where statistics comes in. It enables the sensible handling of uncertainty from sources of error such as random error and systematic error.

The analysis was done by comparing the experimental projection with a simulated projection to look for areas with disagreement in the face of uncertainty. Random error can arise from how x-ray photons are produced in an x-ray tube and how they interact with the additive manufactured product and the x-ray detector. This was modelled by using the compound Poisson distribution. Incorrect simulation of the projection can cause systematic error and this was corrected using the empirical null filter. These sources of error were considered in the comparison of projections with the use of hypothesis testing.

The front cover shows the before and after of the statistical analysis. The left hand side shows an x-ray projection of an additive manufactured cuboid. Its edges appeared curved due to spot and panel effects and this can be fixed using shading correction. The right hand side shows the $p$-values of the resulting inference. Lighter colours show evidence of a defect and they successfully highlighted voids put in there purposefully.

In Chapter \ref{chapter1}, x-ray computed tomography and additive manufacturing is reviewed. Sources of error were looked at and it was investigated to see how they were handled. In Chapter \ref{chapter2}, a test sample was additive manufactured and the chapter describes how experimental x-ray projections were obtained. Shading correction is explained here and it was used to remove sources of systematic errors in the projections. In Chapter \ref{chapter3}, the compound Poisson distribution is studied so that it can be used to model the detection of x-rays. In Chapter \ref{chapter4}, the uncertainty in the projection was quantified using the variance and generalised linear models were used to predict it. In Chapter \ref{chapter5}, novel statistical techniques were developed and implemented to look for defects in the test sample in the face of uncertainty. This was done by comparing the experimental projection with a simulated projection and looking for any disagreement. The empirical null filter was used to cater for any model misspecification so that sensible conclusions were made. The thesis ends with an evaluation in Chapter \ref{chapter6}.

>>>>

The uncertainty of the projection was modelled using a compound Poisson distribution. This arises from x-ray photon arrivals being a Poisson process and each photon has random energy. This results in a linear relationship between the mean and variance of the grey value in the projection. Fitting of the compound Poisson distribution using the expectation-maximisation algorithm was unsuccessful due to identifiability issues with the model. Instead, a gamma-distributed generalised linear model was fitted and used for variance prediction to quantify the uncertainty.

Software, called \emph{aRTist}, was used to simulate the projection and compared with the experimental projection in the face of uncertainty by treating each pixel as a hypothesis test. To overcome the imperfections of the simulation, the empirical null filter was used to cater for model misspecification so that sensible inference was achieved. This was done by locally normalising the test statistics using the mode. Voids with diameters in the order of millimetres were detectable.

@@

The main aim of this thesis is to investigate if it is possible to speed up the quality control process of additive manufactured products by using only a few x-ray projections. By using fewer x-ray projections, uncertainty is introduced. This can be tackled by using statistics because it enables the sensible handling of uncertainty from sources of error such as random error and systematic error.

The analysis was done by comparing the experimental projection with a simulated projection to look for areas with disagreement in the face of uncertainty. Random error can arise from how x-ray photons are produced in an x-ray tube and how they interact with the additive manufactured product and the x-ray detector. This was modelled by using the compound Poisson distribution. Incorrect simulation of the projection contribute to systematic error and this was corrected using the empirical null filter. These sources of error were considered in the comparison of the projections with the use of hypothesis testing.

The front cover shows the before and after of the statistical analysis. The left-hand side shows an x-ray projection of an additive manufactured cuboid. Its edges appeared curved due to spot and panel effects and this can be fixed using shading correction. The right-hand side shows the $p$-values of the resulting inference. Lighter colours show evidence of a defect and they successfully highlighted voids put in there purposefully.

In Chapter \ref{chapter1}, x-ray computed tomography and additive manufacturing is reviewed. Sources of error were investigated and see how they were handled. In Chapter \ref{chapter2}, a test sample was additively manufactured and the chapter describes how experimental x-ray projections were obtained. Shading correction is explained here and it was used to remove sources of systematic error in the projections. In Chapter \ref{chapter3}, the compound Poisson distribution is studied so that it can be used to model the detection of x-rays. In Chapter \ref{chapter4}, the uncertainty in the projection was quantified using the variance and generalised linear models were used to predict it. In Chapter \ref{chapter5}, novel statistical techniques were developed and implemented to look for defects in the test sample in the face of uncertainty. This was done by comparing the experimental projection with a simulated projection and looking for any disagreement. The empirical null filter was used to cater for any model misspecification so that sensible conclusions were made. The thesis ends with an evaluation in Chapter \ref{chapter6}.

### 2019-09-09 reports/thesis/chapters/1_literatureReview.tex
Revise

The different AM technologies can be classified based on the apparatus, for example liquid based or power based, and/or on the method of manufacturing, for example point by point or layer by layer \citep{kruth1991material}. The liquid based AM technologies presented here are stereolithography \citep{kodama1981automatic, hull1986apparatus, 3d2019our} and fused deposition modelling \citep{crump1991fused, crump1992apparatus, stratasys2019what}. The following power based technologies are presented here: 3D printing \citep{sachs1990three}, selective laser sintering \citep{deckard1989method, dtm1990the, 3d2019our}, electron beam melting \citep{larsson2004arrangement, arcam2019history}, laser engineered net shaping \citep{atwood1998laser}. Illustrations of these technologies are shown in Figure \ref{fig:literature_technologies}.

@@

3D printing is a powder based AM technology. A jetting head deposit a binding agent in droplets onto a bed of powder of ceramic, metal or polymer. The binding agent is cured via evaporation or heating which glues the powder particles together. The jetting head can move in the $x-y$ plane and the object is manufactured layer by layer by moving the platform in the $z$ direction and renewing the powder using a roller. The binding agent must have low viscosity so it can be deposited, it may also be charged so that it can be deflected using an electric field for precise deposition \citep{sachs1990three}. The thickness of each layer is determined by the size of the droplets of the binding agent, which can be as small as \SI{15}{\micro\metre} in diameter \citep{sachs1990three}. \cite{sachs1990three} reported a tolerance of 0.001 inches (\SI{0.03}{\milli\metre}).

Selective laser sintering, electron beam melting and laser engineered net shaping are powder based AM technology. Selective laser sintering is similar to 3D printing but instead a laser is used to sinter or fuse the powder particles together. This is done in a chamber heated just below the melting point of the material \citep{wong2012review}. Various materials such as metals and plastics can be used \citep{wong2012review}. Electron beam melting is similar but instead an electron beam is used instead of a laser and this is done in a high vacuum chamber to avoid oxidation \citep{wong2012review}. In laser engineered net shaping, a powder bed is not used; the powder is deposited on the desired location and then melted using a laser, as shown in Figure \ref{fig:literature_lens}. This is a popular method to manufacture metal objects \citep{gibson2010additive}.

@@

There are many more AM technologies but they can be found in numerous review literatures. A comparison of the mentioned AM technologies available at the time were done by \cite{pham1998comparison, kim2008benchmark}. Factors such as material cost, mechanical properties and the resolution of the manufacturing were considered. There are also safety aspects to assess, for example powder in powder based methods can escape into the environment and the liquid used in stereolithography is toxic, sticky and has spilling risk \citep{kim2008benchmark}. This makes fused deposition modelling a popular choice and can be used in an office environment \citep{ngo2018additive}.

@@

The blueprint of the object to be manufactured is called a computer-aided design (CAD) model. For it to be processed by an AM apparatus, the CAD model is converted to a STL file \citep{3d1989sterolithography, 3d2019what} which represent surfaces made up of a series of triangles, an example is shown in Figure \ref{fig:literature_stl}. STL stands for sterolithography but could also be called standard tessellation language \citep{wong2012review}. Some accuracy is lost here as the surface of the CAD model is represented approximately by triangles \citep{gibson2010additive}. The STL file is then sliced into layers \citep{jamieson1995direct, vatani2009enhanced} so that the AM apparatus knows what to build for each layer.

@@

When the AM object is manufactured, post processing techniques can be done at this stage. For example sanding may be done to smooth the surfaces \citep{gibson2010additive}. The manufactured object may be inspected for pores or defects by comparing the x-ray image of the object with the CAD model \citep{lee2015compliance, villarraga2015assessing, kim2016inspection}.

@@

There are various discontinuities in AM. In FDM, a staircase effect on the surface of the product arises from poor slicing methods of the CAD model \citep{weeren1995quality}. Internal voids can be formed due to insufficient material flow \citep{weeren1995quality}. Other factors which can cause defects include misalignment of the platform or nozzle, depletion of material and lack of adhesion due to low temperatures \citep{gunaydin2018common}. There are also problems in the manufacturing of metal parts \citep{everton2016review}. For example gas can become trapped during the manufacturing process forming gas pores in the manufactured object \citep{thijs2010study, tammas2015xct}, they can be \SIrange{5}{20}{\micro\metre} in diameter \citep{everton2016review}. Layers may not fuse together and form elongated pores, this can be fixed by increasing the energy of the beam but too high will cause evaporation of the AM part \citep{mumtaz2008high}. They can be \SIrange{50}{500}{\micro\metre} in size \citep{everton2016review}. They are observable using a scanning electron microscope as shown in Figure \ref{fig:literature_pores}. Low wetting ability of the melt pool can cause balling, this is where the sintered powder has poor contact on the existing layer causing spherical particles to form on the surface of the AM part \citep{li2012balling, gu2009balling}. The spherical particles can vary in size of \SIrange{10}{500}{\micro\metre} \citep{li2012balling}. Low oxygen content in the environment \citep{niu1999instability} and higher energy beams \citep{gu2009balling} can reduce the balling effect. Some examples are shown in Figure \ref{fig:literature_balling} using an electron scanning microscope. Cracks can form due to extreme temperature changes and gradients \citep{mercelis2006residual, zaeh2010investigations}.

@@

The manufacturing process can be monitored, this is called online or in-situ process monitoring \citep{everton2016review}. The idea is that problems in the manufacturing are found as soon as possible before the final product is spoiled \citep{cerniglia2015inspection}. Various methods are used for in-situ process monitoring. Most commonly a high speed camera is installed capturing the various wavelengths in the electromagnetic spectrum emitted by the melt pool \citep{berumen2010quality, craeghs2011online, lott2011design}. Various discontinuities and errors can be detected \citep{clijsters2014in} and be used to give feedback to the AM apparatus \citep{herzog2013method}. Other methods include measuring the surface using a laser \citep{cerniglia2015inspection} and using an infrared camera to measure the temperature of the melt pool \citep{rodriguez2012integration}.

@@

XCT started its use in the medical field but advancement of the technology saw its use in manufacturing and metrology, the science of measurement. Applications of XCT include the examination of acetabular hip prosthesis cups \citep{kourra2018computed}, skeletons \citep{appleby2014scoliosis}, batteries \citep{taiwo2017investigating} and materials \citep{zhang2016x, wang2017x}. XCT can be used to reverse engineer existing products and improved. The improved can be fabricated using AM, for example, it was used for improving existing hollow engine valves \citep{cooper2015design}. However the use of XCT in metrology is not yet firmly established compared to other methods of measurement \citep{thompson2016x}. This is because there is a lot of inconsistencies in the setup of XCT apparatuses and on controlling the sources of error.

@@

The setup of XCT \citep{cormack1973reconstruction, hounsfield1973computerized, hounsfield1980computed} in the medical field involves the patient laying on a flat bed. An x-ray source and x-ray detector pair rotate around and translate along the patient to get readings of the x-rays after attenuating through the patient using different paths. X-ray beams were pencil beams in the early versions of XCT \citep{michael2001x}. To reduce scanning times, fan shaped beams and arrays of detectors were used and they can move in a spiral fashion along and around the patient \citep{cierniak2011x}. These multiple x-ray readings can be used to reconstruct a representation of the patient in 3D \citep{zeng2010medical}. This is illustrated in Figure \ref{fig:literature_medicalct}.

@@

The patient cannot be exposed to too much radiation, therefore the x-rays used are of low power. This can cause noisy readings from the detector. The sources of noise are from the behaviour of the x-rays and from the electronics in the detector \citep{yang2010noise}. In this realm of low signal to noise ratio, the noise has a compound Poisson element to it \citep{whiting2002signal, whiting2006properties}. Many reconstruction algorithms have been proposed to take the compound Poisson noise into consideration \citep{elbakri2002statistical, elbakri2003efficient, elbakri2003statistical, lasio2007statistical, xie2008x}.

@@

In manufacturing and metrology, high power x-rays can be used in XCT because there is no consequence of the manufactured object absorbing the radiation. The XCT setup is different, the object is held by foam on a turntable and placed between an x-ray source and an x-ray detector. X-ray projections are taken while the object rotates. Typically the x-ray is a cone beam \citep{kruth2011computed}. This is illustrated in Figure \ref{fig:literature_xct}.

@@

The electrons can interact with the anode in a number of ways. The electrons can be deflected or decelerated due to the electric field from the nucleus of the target anode material. The energy lost by the electrons is emitted as bremsstrahlung radiation. It depends on the potential difference in the x-ray tube, as this determines the energy of the fired electrons, and also the proton number of the anode target because this affects the electric field produced by the nucleus in the anode target \citep{sun2012overview}. Another interaction is when the electrons may collide with the nucleus in the anode target, exciting an inner shell electron and ionizing it. This produce a vacancy in the electron shell and emits a photon when the excited electron drops down back to the ground state. This is known as characteristic radiation and the energy emitted is discrete and depends on the material in the anode target \citep{sun2012overview}.

The efficiency of an x-ray tube is poor. 99\% of the energy from electrons is converted to heat, the rest to x-rays \citep{kruth2011computed}.

@@

The scanned object is exposed to x-ray photons which undergo attenuation when interacting with the object in a number of ways \citep{cantatore2011introduction}. The object can absorb the photons via the photoelectric effect. In the photoelectric effect, the photons transfer all its energy to a bounded electron and ejects it from the object's atom \citep{millikan1916direct}. Photons can be scattered by the object by colliding inelastically with and transfers its energy to an electron. This process is known as Compton scattering \citep{compton1923quantum}. The photoelectric effect and Compton scattering make a number of photons undetectable. However if some of the photons avoid these processes, they are detected and their energy is left unaffected.

Beer's law simplifies these quantum mechanistic process. Suppose the x-ray beam with rate of emission $I_0$ is mono-energetic and travels in a straight line in the $x$-axis. Let $\mu(x)$ be the attenuation coefficient of the object and the x-ray beam has rate of emission $I$ after attenuation. A differential equation can be set up to model the decay of photons as it attenuate through the object such that
\begin{equation}
\dfrac{\diff I}{\diff x} = -I\mu(x)
\end{equation}
which can be solved
\begin{equation}
I = I_0\exp\left[\int_{x \in \text{path of photon}}-\mu(u)\diff u\right] \ .
\label{eq:beerLaw}
\end{equation}
However, the photoelectric effect and Compton scattering, thus the attenuation coefficient as well, depends on the energy of the photons \citep{elbakri2002statistical}. Therefore $\mu(x,E)$ should be made dependent on the energy of the photons \citep{cantatore2011introduction} and can cause some inaccuracies in Beer's law. In general low energy photons are more likely to be absorbed and scattered than high energy photons, which increases the average energy of the detected photons \citep{sun2012overview}. This is called beam hardening.

@@

Not all of the visible light pulses are detected by the photodiodes, thus not all the x-ray photons are detected. The ratio between the number of x-ray photons detected by the detector and the number of x-ray photons arriving at the detector is called the quantum efficiency \citep{cierniak2011x, ren2018tutorial}. This makes the detection a two stage process, converting the x-ray photons into visible light which are then detected \citep{cierniak2011x}. There exist equipment which detects x-ray directly such as a xenon gas ionization detector \citep{fuchs2000direct} but this is unrivalled by solid state CT systems, such as sintillator-photodiodes detectors, which have high quantum efficiency of about 98\% to 99.5\% \citep{hsieh2000investigation}.

Once multiple projections of the object have been acquired at multiple angles, the reconstruction process can start. The objective of reconstruction is to estimate the attenuation coefficient of the object at each point in space $\mu(x,y,z)$ using the x-ray projections. This is done using the fact that the projections are based on the line integral of the attenuation coefficient along the path of photons. This problem was formed by \cite{radon1986on} as the `determination of functions from their integral values along certain manifolds'.

@@

There are many variables in XCT and a lot of them have to be controlled. For example XCT should be done in room temperature to avoid any thermal variation \citep{bryan1990international}, however this can be hard to do when the x-ray tube is a heat source \citep{kruth2011computed}.

The set up of XCT has a number of variables. The potential difference and current of the x-ray tube can be adjusted to control the contrast and brightness of the x-ray projection. The exposure time is also a factor. These settings should be set high enough to avoid beam extinction but low enough that there is contrast where less material is present \citep{kruth2011computed}. The magnification can be modified by altering the distances between the x-ray tube, the object and the x-ray detector. Increasing the magnification increases the image resolution but can cause blurry images, this is the result from using an x-ray source with a finite spot size as shown in Figure \ref{fig:literature_magnification} \citep{kruth2011computed}. Larger spot sizes cause more blurry results, this is known as the penumbra effect \citep{kueh2016modelling}. However, spot sizes too small can produce concentrated heat \citep{welkenhuyzen2009industrial} and can damage the x-ray tube.

@@

All of the parameters of XCT discussed can be determined before the XCT process by use of simulations \citep{reisinger2011simulation, reiter2011simulation}, however there may be inconsistencies. For example even though the target material of the anode and power is specified, the energy spectrum can still vary \citep{stumbo2004direct}.

Problems can occur in the detector. For example, pixels in the acquired projection can be defected or dead \citep{brettschneider2014spatial} and the panel structure of the detector can be observed \citep{yang2009evaluation}. Another problem is that there exist spatially correlated noise within a projection which can detected experimentally \citep{sun2016characterisation} as well as correlation between acquisitions, known as image lag \citep{yang2009evaluation}. Precautions can be taken reduce the impact from image lag such as waiting for 20 minutes between acquisitions \citep{yang2010noise}.

@@

One of the disadvantages of XCT is that it is a slow process. XCT is not an instantaneous process so progress bars are usually featured in XCT marketing such as \cite{nikon2015inline}'s inline quality control. The reconstruction can take between 5 minutes to a number of hours \citep{warnett2016towards}. More angular projections would take more time but will improve the accuracy of the reconstruction \citep{kruth2011computed}. \cite{warnett2016towards} improved the speed of XCT by sacrificing accuracy of the reconstruction. This was done by placing the object to scan on a conveyor belt surrounded by multiple x-ray source and detector pairs as shown in Figure \ref{fig:literature_conveyor}. Fewer angular projections were taken but they can be obtained in one go, speeding up the process.

>>>>

The different AM technologies can be classified based on the apparatus, for example liquid based or powder based, and/or on the method of manufacturing, for example point by point or layer by layer \citep{kruth1991material}. The liquid based AM technologies presented here are stereolithography \citep{kodama1981automatic, hull1986apparatus, 3d2019our} and fused deposition modelling \citep{crump1991fused, crump1992apparatus, stratasys2019what}. The following powder based technologies are presented here: 3D printing \citep{sachs1990three}, selective laser sintering \citep{deckard1989method, dtm1990the, 3d2019our}, electron beam melting \citep{larsson2004arrangement, arcam2019history}, laser engineered net shaping \citep{atwood1998laser}. Illustrations of these technologies are shown in Figure \ref{fig:literature_technologies}.

@@

3D printing is a powder based AM technology. A jetting head deposit a binding agent in droplets onto a bed of powder of ceramic, metal or polymer. The binding agent is cured via evaporation or heating which glues the powder particles together. The jetting head can move in the $xy$-plane and the object is manufactured layer by layer by moving the platform in the $z$-axis and renewing the powder using a roller. The binding agent must have low viscosity so it can be deposited and may also be charged so that it can be deflected using an electric field for precise deposition \citep{sachs1990three}. The thickness of each layer is determined by the size of the droplets of the binding agent, which can be as small as \SI{15}{\micro\metre} in diameter \citep{sachs1990three}. \cite{sachs1990three} reported a tolerance of 0.001 inches (\SI{0.03}{\milli\metre}).

Selective laser sintering, electron beam melting and laser engineered net shaping are powder based AM technology. Selective laser sintering is similar to 3D printing, but instead, a laser is used to sinter or fuse the powder particles together in a chamber heated just below the melting point of the material \citep{wong2012review}. Various materials such as metals and plastics can be used \citep{wong2012review}. Electron beam melting is similar, but instead of a laser, an electron beam is used. This is done in a high vacuum chamber to avoid oxidation \citep{wong2012review}. In laser engineered net shaping, a powder bed is not used; the powder is deposited on the desired location and then melted using a laser, as shown in Figure \ref{fig:literature_lens}. This is a popular method to manufacture metal objects \citep{gibson2010additive}.

@@

There are many more AM technologies but they can be found in numerous review literatures. A comparison of the mentioned AM technologies available at the time were done by \cite{pham1998comparison, kim2008benchmark}. Factors such as material cost, mechanical properties and the resolution of the manufacturing were considered. There are also safety aspects to assess, for example, powder in powder based methods can escape into the environment and the liquid used in stereolithography is toxic, sticky and has spilling risk \citep{kim2008benchmark}. This makes fused deposition modelling a popular choice and can be used in an office environment \citep{ngo2018additive}.

@@

The blueprint of the object to be manufactured is called a computer-aided design (CAD) model. For it to be processed by an AM apparatus, the CAD model is converted to a STL file \citep{3d1989sterolithography, 3d2019what} which represent surfaces by a series of triangles, an example is shown in Figure \ref{fig:literature_stl}. STL stands for sterolithography but could also be called standard tessellation language \citep{wong2012review}. Some accuracy is lost here as the surface of the CAD model is represented approximately by triangles \citep{gibson2010additive}. The STL file is then sliced into layers \citep{jamieson1995direct, vatani2009enhanced} so that the AM apparatus knows what to build for each layer.

@@

When the AM object is manufactured, post processing techniques can be done at this stage. For example, sanding may be done to smooth the surfaces \citep{gibson2010additive}. The manufactured object may be inspected for pores or defects by comparing the x-ray projection of the object with the CAD model \citep{lee2015compliance, villarraga2015assessing, kim2016inspection}.

@@

There are various discontinuities in AM. In FDM, a staircase effect on the surface of the product arises from poor slicing methods of the CAD model \citep{weeren1995quality}. Internal voids can be formed due to insufficient material flow \citep{weeren1995quality}. Other factors which can cause defects include misalignment of the platform or nozzle, depletion of material and lack of adhesion due to low temperatures \citep{gunaydin2018common}.

There are also problems in the manufacturing of metal parts \citep{everton2016review}, for example, gas can become trapped during the manufacturing process forming gas pores in the manufactured object \citep{thijs2010study, tammas2015xct}. These gas pores can be \SIrange{5}{20}{\micro\metre} in diameter \citep{everton2016review}.

Layers may not fuse together and form elongated pores. This can be fixed by increasing the energy of the beam but too increasing it too much will cause evaporation of the AM part \citep{mumtaz2008high}. These pores can be \SIrange{50}{500}{\micro\metre} in size \citep{everton2016review} and can be observed using a scanning electron microscope as shown in Figure \ref{fig:literature_pores}.

Low wetting ability of the melt pool can cause balling which is where the sintered powder has poor contact on the existing layer causing spherical particles to form on the surface of the AM part \citep{li2012balling, gu2009balling}. The spherical particles can vary in size of \SIrange{10}{500}{\micro\metre} \citep{li2012balling}. The balling effect can be reducted by ensuring low oxygen content in the environment \citep{niu1999instability} and using higher energy beams \citep{gu2009balling}. Some examples are shown in Figure \ref{fig:literature_balling} using an electron scanning microscope.

Cracks can form due to extreme temperature changes and gradients \citep{mercelis2006residual, zaeh2010investigations}.

@@

The manufacturing process can be monitored, this is called online or in-situ process monitoring \citep{everton2016review}. The idea is that problems during the manufacturing processare found as soon as possible before the final product is spoiled \citep{cerniglia2015inspection}. Various methods are used for in-situ process monitoring, for example, a high speed camera can be installed to capture the various wavelengths in the electromagnetic spectrum emitted by the melt pool \citep{berumen2010quality, craeghs2011online, lott2011design}. Various discontinuities and errors can be detected \citep{clijsters2014in} and be used to give feedback to the AM apparatus \citep{herzog2013method}. Other methods include measuring the surface using a laser \citep{cerniglia2015inspection} and using an infrared camera to measure the temperature of the melt pool \citep{rodriguez2012integration}.

@@

XCT started its use in the medical field but advancement of the technology saw its use in manufacturing and metrology, the science of measurement. Applications of XCT include the examination of acetabular hip prosthesis cups \citep{kourra2018computed}, skeletons \citep{appleby2014scoliosis}, batteries \citep{taiwo2017investigating} and materials \citep{zhang2016x, wang2017x}. XCT can be used to reverse engineer existing products and improvements can be fabricated using AM, for example, it was used for improving existing hollow engine valves \citep{cooper2015design}. However, the use of XCT in metrology is not yet firmly established compared to other methods of measurement \citep{thompson2016x}. This is because there are a lot of inconsistencies in the setup of XCT apparatuses and on controlling the sources of error.

@@

The setup of XCT \citep{cormack1973reconstruction, hounsfield1973computerized, hounsfield1980computed} in the medical field involves the patient laying on a flat bed. An x-ray source and x-ray detector pair rotate around and translate along the patient to get readings of the x-rays after attenuating through the patient via different paths. X-ray beams were pencil beams in the early versions of XCT \citep{michael2001x}. To reduce scanning times, fan shaped beams and arrays of detectors were used and they can move in a spiral fashion along and around the patient \citep{cierniak2011x}. These multiple x-ray readings can be used to reconstruct a representation of the patient in 3D \citep{zeng2010medical}. This is illustrated in Figure \ref{fig:literature_medicalct}.

@@

The patient cannot be exposed to too much radiation, therefore the x-rays used are of low power which can cause noisy readings from the detector. The sources of noise are from the behaviour of the x-rays and from the electronics in the detector \citep{yang2010noise}. In this realm of low signal to noise ratio, the noise has a compound Poisson element to it \citep{whiting2002signal, whiting2006properties}. Many reconstruction algorithms have been proposed to take the compound Poisson noise into consideration \citep{elbakri2002statistical, elbakri2003efficient, elbakri2003statistical, lasio2007statistical, xie2008x}.

@@

In manufacturing and metrology, high power x-rays can be used in XCT because there is no consequence of the manufactured object absorbing the radiation. As a result, the XCT setup is different. The object is held by foam on a turntable and placed between an x-ray source and an x-ray detector. X-ray projections are taken while the object rotates. Typically the x-ray is a cone beam \citep{kruth2011computed}. This is illustrated in Figure \ref{fig:literature_xct}.

@@

The electrons can interact with the anode in a number of ways. The electrons can be deflected or decelerated due to the electric field from the nucleus of the target anode material. The energy lost by the electrons is emitted as bremsstrahlung radiation. The energy of the radiation depends on the potential difference in the x-ray tube, as this determines the energy of the fired electrons, and also the proton number of the anode target because this affects the electric field produced by the nucleus in the anode target \citep{sun2012overview}. Another interaction is when the electrons may collide with the nucleus in the anode target, exciting an inner shell electron and ionizing it. This produce a vacancy in the electron shell and emits a photon when the excited electron drops down back to the ground state. This is known as characteristic radiation and the energy emitted is discrete and depends on the material in the anode target \citep{sun2012overview}.

The efficiency of an x-ray tube is poor. Over 99\% of the energy from electrons is converted to heat, the rest to x-rays \citep{kruth2011computed}.

@@

The scanned object is exposed to x-ray photons which undergo attenuation when interacting with the object in a number of ways \citep{cantatore2011introduction}. The object can absorb the photons via the photoelectric effect. In the photoelectric effect, the photons transfer all of its energy to a bounded electron and ejects it from the atom in the object \citep{millikan1916direct}. Photons can be scattered by the object by colliding inelastically with, and transfers its energy to, an electron. This process is known as Compton scattering \citep{compton1923quantum}. The photoelectric effect and Compton scattering cause a number of photons to be undetectable. If some of the photons avoid these processes, they are detected and their energy is left unaffected.

Beer's law simplifies these quantum mechanistic process. Suppose the x-ray beam with rate of emission $I_0$ is mono-energetic and travels in a straight line in the $x$-axis. Let $\mu(x)$ be the attenuation coefficient of the object and the x-ray beam has rate of emission $I$ after attenuation. A differential equation can be set up to model the decay of photons as it attenuate through the object such that
\begin{equation}
\dfrac{\diff I}{\diff x} = -I\mu(x)
\end{equation}
which can be solved
\begin{equation}
I = I_0\exp\left[\int_{x \in \text{path of photon}}-\mu(x)\diff x\right] \ .
\label{eq:beerLaw}
\end{equation}
However, the photoelectric effect and Compton scattering, thus the attenuation coefficient as well, depends on the energy of the photons \citep{elbakri2002statistical}. Therefore $\mu(x,E)$ should be made dependent on the energy of the photons \citep{cantatore2011introduction} and can cause some inaccuracies in Beer's law. In general low energy photons are more likely to be absorbed and scattered than high energy photons, which increases the average energy of the detected photons \citep{sun2012overview}. This is called beam hardening.

@@

Not all of the visible light pulses are detected by the photodiodes, thus not all the x-ray photons are detected. The ratio between the number of x-ray photons detected by the detector and the number of x-ray photons arriving at the detector is called the quantum efficiency \citep{cierniak2011x, ren2018tutorial}. This makes the detection a two stage process, converting the x-ray photons into visible light which are then detected \citep{cierniak2011x}. There exist equipment which detects x-ray directly such as a xenon gas ionisation detector \citep{fuchs2000direct} but this is unrivalled by solid state CT systems, such as sintillator-photodiodes detectors, which have high quantum efficiency of about 98\% to 99.5\% \citep{hsieh2000investigation}.

Once projections of the object have been acquired at multiple angles, the reconstruction process can start. The objective of reconstruction is to estimate the attenuation coefficient of the object at each point in space $\mu(x,y,z)$ using the x-ray projections. This is done using the fact that the projections are based on the line integral of the attenuation coefficient along the path of photons. This problem was formed by \cite{radon1986on} as the `determination of functions from their integral values along certain manifolds'.

@@

There are many variables in XCT and a lot of them have to be controlled, for example, XCT should be done in room temperature to avoid any thermal variation \citep{bryan1990international}, however this can be hard to do when the x-ray tube is a heat source \citep{kruth2011computed}.

The potential difference and current of the x-ray tube can be adjusted to control the contrast and brightness of the x-ray projection. The exposure time is also a factor. These settings should be set high enough to avoid beam extinction but low enough that there is contrast where less material is present \citep{kruth2011computed}.

The magnification can be modified by altering the distances between the x-ray tube, the object and the x-ray detector. Increasing the magnification increases the image resolution but can cause blurry images, this is the result from using an x-ray source with a finite spot size as shown in Figure \ref{fig:literature_magnification} \citep{kruth2011computed}. Larger spot sizes cause more blurry results, this is known as the penumbra effect \citep{kueh2016modelling}. However, spot sizes too small can produce concentrated heat \citep{welkenhuyzen2009industrial} and can damage the x-ray tube.

@@

All of the parameters of XCT discussed can be determined before the XCT process by use of simulations \citep{reisinger2011simulation, reiter2011simulation}, however, there may be inconsistencies. For example, even though the target material of the anode and power is specified, the energy spectrum can still vary \citep{stumbo2004direct}.

Problems can occur in the detector, for example, pixels in the acquired projection can be defected or dead \citep{brettschneider2014spatial} and the panel structure of the detector can be observed \citep{yang2009evaluation}. Another problem is that there exist spatially correlated noise within a projection which can be detected experimentally \citep{sun2016characterisation} as well as correlation between acquisitions, known as image lag \citep{yang2009evaluation}. Precautions can be taken reduce the impact from image lag such as waiting for 20 minutes between acquisitions \citep{yang2010noise}.

@@

One of the disadvantages of XCT is that it is a slow process. XCT is not an instantaneous process so progress bars are usually featured in XCT marketing such as \cite{nikon2015inline}'s inline quality control. The reconstruction can take between 5 minutes to a number of hours \citep{warnett2016towards}. More angular projections would take more time but will improve the accuracy of the reconstruction \citep{kruth2011computed}. \cite{warnett2016towards} improved the speed of XCT by sacrificing accuracy of the reconstruction. This was done by placing the object on a conveyor belt surrounded by multiple x-ray source and detector pairs as shown in Figure \ref{fig:literature_conveyor}. Fewer angular projections were taken but they can be obtained in one go, speeding up the process.
